Word learning at the semantics pragmatics interface

### 2020-04-17 paper/bda_fig.tex
reorganize repo and add bda figure to supplement
add rsa eqns to bda fig; add some priors

	\node[det, above=of data_me](L1_me){$L'_1$};
	\node[det, above=of data_comb](L1_comb){$L_1$};
	\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

@@

%	\plate{plate_data_me}{
%		(data_me)
%	}{$i \in \mathcal{P}_{1}$}

%	\plate{plate_data_cg}{
%		(data_cg)
%	}{$i \in \mathcal{P}_{2}$}

@@

>>>>

\node[det, above=of data_me](L1_me){$L'$};
\node[det, above=of data_comb](L1_comb){$L$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

@@

\

@@

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,5) { 
$\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
$\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ \\
$\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
 $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ \\
 $\mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
 $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ \\
 $\sigma^\theta_1 \sim \text{Uniform}(0,1)$
};

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ $P_{L}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\ 
$P_{S}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} $\\
$P(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})$
};
